### 2024-05-26 2024-5-13/sections/implementation.tex
add data

\subsubsection{Empirical justification of the heuristics} We compare the performance of $\ostrichrecl$ with $\ostrichrecl_{\rm -NEST}$, $\ostrichrecl_{\rm -COMP}$, $\ostrichrecl_{\rm -FIND}$, and $\ostrichrecl_{\rm -ALL}$ where $\ostrichrecl_{\rm -NEST}$ is obtained from $\ostrichrecl$ by removing the heuristic for nested counting, $\ostrichrecl_{\rm -COMP}$ is obtained from $\ostrichrecl$ by removing the heuristic for complement on counting operators, $\ostrichrecl_{\rm -FIND}$ is obtained from $\ostrichrecl$ by removing the heuristic for finding the accepted word of the automaton, and $\ostrichrecl_{\rm -ALL}$ is obtained from $\ostrichrecl$ by removing all the heuristics.
The experiment results can be found in Table~\ref{tab:results_heuristic}.

>>>>

\subsubsection{Empirical justification of the heuristics} We compare the performance of $\ostrichrecl$ with ${\rm -NEST}$, ${\rm -COMP}$, ${\rm -FIND}$, and ${\rm -ALL}$ where ${\rm -NEST}$ is obtained from $\ostrichrecl$ by removing the heuristic for nested counting, ${\rm -COMP}$ is obtained from $\ostrichrecl$ by removing the heuristic for complement on counting operators, ${\rm -FIND}$ is obtained from $\ostrichrecl$ by removing the heuristic for finding the accepted word of the automaton, and ${\rm -ALL}$ is obtained from $\ostrichrecl$ by removing all the heuristics.
The experiment results can be found in Table~\ref{tab:results_heuristic}.
